---
title: "rapExplorer"
format: html
editor: visual
---

## Basic outline of app:

user selects:

-   number of taxa

    -   drop down

-   absolute abundances of each taxa

    -   text box for each number of taxa?

    -   one set for "control" and one set for "experimental"

app produces:

-   2 barplots of absolute abundances, control and experimental

-   2 stacked barplots of relative abundances in each sample

-   a table that displays:

    -   species richness

    -   Shannon diversity

    -   Simpson index

    -   Shannon(?) Evenness

-   another table that shows

    -   dif in relative abundance for each taxa

    -   log fold change ratio of control and experimental groups

```{r}
species_names <- c("A", "B", "C", "D", "E")
control       <- c(20, 100, 10, 40, 80) 
experimental  <- c(20, 90, 80, 10, 60)
experimental2 <- c(200, 900, 800, 100, 600)


df_counts <- data.frame(control, experimental)
df_counts_diff_depth <- data.frame(control, experimental)
```

```{r}

#install.packages("abdiv")
library(abdiv)
library(tidyverse)

```

```{r}
simpson_cont <- round(simpson(x = control),         3)
simpson_exp  <- round(simpson(x = experimental),    3)
simpson_exp2 <- round(simpson(x = experimental2),   3)


simpson_even_cont  <- round(simpson_e(x = control),       3)
simpson_even_exp   <- round(simpson_e(x = experimental),  3)
simpson_even_exp   <- round(simpson_e(x = experimental2), 3)

```

```{r}
calculate_rel_abund <- function(counts_i) {
  counts_total <- sum(counts_i)
  proportions <- counts_i / counts_total
  rounded_proportions <- round(proportions, 3)
  return(rounded_proportions)
}

```

```{r}
rel_abund_cont <- calculate_rel_abund(control)
rel_abund_exp  <- calculate_rel_abund(experimental)
rel_abund_exp2 <- calculate_rel_abund(experimental2)

df <- data.frame(species_names, rel_abund_cont, rel_abund_exp, rel_abund_exp2)
df<- df %>% 
  pivot_longer(-species_names, names_to = "treatment")

df
```

```{r}

df %>% 
  group_by(species_names) %>% 
  ggplot(aes(x = treatment, y = value, fill = species_names)) +
  geom_col()

```
